
---
title: "Curriculum Vitae"
---



## Education

 

```{r,echo=F}
education = rio::import("cv.xlsx", sheet = "Education")
eductags = htmltools::tagList()

for (i in 1:nrow(education)) {
  edu = education[i,]
  eductags[[i]] <- htmltools::tags$li(
    htmltools::tagList(
      htmltools::tags$span(paste0("(",edu$Year,") ")),
      htmltools::tags$strong(edu$Program), 
      htmltools::tags$span(paste0(" - ", edu$Institution)),
      htmltools::tags$span(paste0(ifelse(!is.na(edu$Extra),paste0("", edu$Extra),"")))
    )
  )
}
htmltools::tags$ul(
eductags
)
```



 
## Work Experience


```{r,echo=F}
experience = rio::import("cv.xlsx", sheet = "Experience")
exptags = htmltools::tagList()

for (i in 1:nrow(experience)) {
  exp = experience[i,]
  exptags[[i]] <- htmltools::tags$li(
    htmltools::tagList(
      htmltools::tags$span(paste0("(",exp$Year,") ")),
      htmltools::tags$strong(ifelse(i==1,htmltools::tagList(htmltools::tags$u(exp$Position)),exp$Position)), 
      htmltools::tags$span(paste0(" - ", exp$Institution)) 
    )
  )
}
htmltools::tags$ul(
exptags
)
```

## Teaching

```{r,echo=F}
teaching = rio::import("cv.xlsx", sheet = "Teaching")
teatags = htmltools::tagList()

for (i in 1:nrow(teaching)) {
  tea = teaching[i,]
  teatags[[i]] <- htmltools::tags$li(
    htmltools::tagList(
      htmltools::tags$span(paste0("(",tea$Year,") ")),
      htmltools::tags$strong(tea$Course), 
      htmltools::tags$span(paste0(" - ", tea$Institution)) 
    )
  )
}
htmltools::tags$ul(
teatags
)
```

## Supervision


```{r,echo=F}
supervision = rio::import("cv.xlsx", sheet = "Supervision")
supervisiontags = htmltools::tagList()

for (i in 1:nrow(supervision)) {
  superv = supervision[i,]
  supervisiontags[[i]] <- htmltools::tags$li(
    htmltools::tagList(
      htmltools::tags$span(superv), 
    )
  )
}
htmltools::tags$ul(
supervisiontags
)
```

## Research Funding

```{r,echo=F}
funding = rio::import("cv.xlsx", sheet = "Funding")
fundingtags = htmltools::tagList()

for (i in 1:nrow(funding)) {
  fund = funding[i,]
  fundingtags[[i]] <- htmltools::tags$li(
    htmltools::tagList(
      htmltools::tags$span(paste0("(",fund$Year,") ")), 
      htmltools::tags$strong(fund$By),  htmltools::tags$br(),
      ifelse(!is.na(fund$Role),htmltools::tagList(list(htmltools::tags$strong("Role:"), htmltools::tags$span(fund$Role),  htmltools::tags$br())),
      htmltools::tagList()),
      ifelse(!is.na(fund$Project),
             htmltools::tagList(list(htmltools::tags$strong("Project name:"), htmltools::tags$span(fund$Project),  htmltools::tags$br())),
              htmltools::tagList()),
      ifelse(!is.na(fund$Amount),
             htmltools::tagList(list(htmltools::tags$strong("Amount:"), htmltools::tags$span(fund$Amount),  htmltools::tags$br())),
             htmltools::tagList())
    )
    )
}
htmltools::tags$ul(
fundingtags
)
```



## Recent reviews / evaluations / industry collaborations
```{r,echo=F}
collabs = rio::import("cv.xlsx", sheet = "Recent_collabs")
collabstags = htmltools::tagList()

for (i in 1:nrow(collabs)) {
  collab = collabs[i,]
  collabstags[[i]] <- htmltools::tags$li(htmltools::tagList(
   htmltools::tags$span( paste0("(",collab$Year,") ")),
   htmltools::tags$span(  collab$Description)
  ))
}

htmltools::tags$ul(
  collabstags
)
```

## Research Visits
```{r,echo=F}
visits = rio::import("cv.xlsx", sheet = "Research_visits")
visitstags = htmltools::tagList()

for (i in 1:nrow(visits)) {
  visit = visits[i,]
  visitstags[[i]] <- htmltools::tags$li(htmltools::tagList(
   htmltools::tags$span( paste0("(",visit$Year,") ")),
   htmltools::tags$strong(  visit$Institution), 
   htmltools::tags$span( paste0(" - ", visit$Country))
  ))
}
htmltools::tags$ul(
visitstags
)
```

## Awards

```{r,echo=F}
awards = rio::import("cv.xlsx", sheet = "Awards")
awardstags = htmltools::tagList()

for (i in 1:nrow(awards)) {
  awa = awards[i,]
  awardstags[[i]] <- htmltools::tags$li(
    paste0("(",awa$Year,") ",awa$Description)
  )
}
htmltools::tags$ul(
awardstags
)
```

## Key academic merits and roles

```{r,echo=F}
editorial = rio::import("cv.xlsx", sheet = "Editorial_work")
editorialtags = htmltools::tagList()

for (i in 1:nrow(editorial)) {
  edi = editorial[i,]
  editorialtags[[i]] <- htmltools::tags$li(htmltools::tagList(
   htmltools::tags$span( paste0("(",edi$Year,") ")),
   htmltools::tags$strong( edi$Position),
   htmltools::tags$span( paste0( " - ", edi$Where))
  ))
}
htmltools::tags$ul(
editorialtags
)
```



## Peer review
Reviewed articles for many international scientific publications such as 
```{r,echo=F}
peer = rio::import("cv.xlsx", sheet = "Peer")$Publication
peertags = htmltools::tagList()

for (i in 1:length(peer)) {
  pe = peer[i]
  peertags[[i]] <- htmltools::HTML(paste0("<span style='margin-right: 2px;' class='badge rounded-pill bg-light'>",peer[i],"</span>"))
}

htmltools::tags$div(
  peertags
)
```
## Projects

Has successfully participated in or managed the following projects that included planning, documentation, collaboration with different departments and colleagues and stakeholders for optimum operation.


```{r,echo=F}
projects = rio::import("cv.xlsx", sheet = "Projects")
projtags = htmltools::tagList()
for (i in 1:nrow(projects)) {
  proj = projects[i,]
  if (!is.na(proj$Year) & !is.na(proj$Name) & ("Unknown" != (proj$Name))){
    projtags[[i]] <- htmltools::tags$li(
      htmltools::tagList(
        htmltools::tags$span(paste0("(",proj$Year,") ")),
        htmltools::tags$strong(proj$Name), 
        htmltools::tags$span(paste0(" -  ", proj$Institution)), 
        htmltools::tags$br(),
        htmltools::tags$small(ifelse(!is.na(proj$Description),proj$Description,""),
        htmltools::tags$br(),htmltools::tags$br()
        )
      )
    )
  }
}
htmltools::tags$ul(
projtags
)
```

 
 
 

 
 

